Titeln på avhandlingens språk

### 2022-09-01 model.tex
figure explanation

\begin{table}[]
\centering
\caption{Default bins used for model parameter levels.}
\label{tab:defaultbins}
% \resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Parameter} & \textbf{Low}     & \textbf{Medium}      & \textbf{High}         \\ \midrule
Neuroticism        & \( [0, 0.5) \)   &                      & \( [0.5, 1.0] \)      \\
Impairment         & \( [0, 1.482) \) & \( [1.482, 3.198) \) & \( [3.198, \infty) \) \\
Duration           & \( [0, 5) \)     & \( [5, 10) \)        & \( [10, \infty) \)    \\ \bottomrule
\end{tabular}%
% }
\end{table}

@@

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.
Finally, in \cref{alg:timings} we present a step-by-step breakdown of how this data is subsequently used to generate realistic execution times.
In plain English, a model which uses this processed data to generate execution times needs to maintain variables for duration, previous impairment, and most recent transition.
At the beginning of each step, the model
\begin{enumerate}
    \item Checks whether any change in impairment has occurred.
    If it has, it resets duration to \num{1} and updates the transition variable accordingly.
    If not, it increases the duration variable by one unless that increase causes it to exceed the threshold of steps required to forget a transition.
    If that's the case, instead the model resets duration to \num{1} and sets the transition variable to ``no transition''.
    \item Discretizes the updated duration value.
    \item Finds all samples with binned neuroticism, impairment, duration, and transition values matching the current state of the system.
    \item Randomly samples the filtered data to obtain a realistic execution time value.
    \begin{itemize}
        \item Alternatively, a distribution can be first be fitted to the filtered samples.
        The model then samples the theoretical distribution instead of the empirical samples.
    \end{itemize}
    \item Finally, updates the stored impairment value with the new impairment and proceeds to the next step.
\end{enumerate}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}\\
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
    }\label{fig:timing}
\end{figure*}

>>>>

\begin{table}[]
\centering
\caption{%
    Default bins used for model parameter levels.
    For impairment, values were rounded to three decimal places.
}
\label{tab:defaultbins}
% \resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Parameter} & \textbf{Low}     & \textbf{Medium}      & \textbf{High}         \\ \midrule
Neuroticism        & \( [0, 0.5) \)   &                      & \( [0.5, 1.0] \)      \\
Impairment         & \( [0, 1.482) \) & \( [1.482, 3.198) \) & \( [3.198, \infty) \) \\
Duration           & \( [0, 5) \)     & \( [5, 10) \)        & \( [10, \infty) \)    \\ \bottomrule
\end{tabular}%
% }
\end{table}

@@

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.
Specifically, we showcase how
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and}}]
    \item higher neuroticism leads to higher mean execution times as impairment goes up (\cref{fig:timing:impneurvsetime})
    \item duration has both a speed-up and slow-down effect on execution times, depending on the level of impairment (\cref{fig:timing:durvsetime})
    \item transitions from higher to lower levels of impairment lead to higher mean execution times when compared to steps far away from a transition, or from a transition from lower to higher levels of impairment (\cref{fig:timing:imptransvsetime})
\end{enumerate*}.

Finally, in \cref{alg:timings} we present a step-by-step breakdown of how this data is subsequently used to generate realistic execution times.
In plain English, a model which uses this processed data to generate execution times needs to maintain variables for duration, previous impairment, and most recent transition.
At the beginning of each step, the model
\begin{enumerate}
    \item Checks whether any change in impairment has occurred.
    If it has, it resets duration to \num{1} and updates the transition variable accordingly.
    If not, it increases the duration variable by one unless that increase causes it to exceed the threshold of steps required to forget a transition.
    If that's the case, instead the model resets duration to \num{1} and sets the transition variable to ``no transition''.
    \item Discretizes the updated duration value.
    \item Finds all samples with binned neuroticism, impairment, duration, and transition values matching the current state of the system.
    \item Randomly samples the filtered data to obtain a realistic execution time value.
    \begin{itemize}
        \item Alternatively, a distribution can be first be fitted to the filtered samples.
        The model then samples the theoretical distribution instead of the empirical samples.
    \end{itemize}
    \item Finally, updates the stored impairment value with the new impairment and proceeds to the next step.
\end{enumerate}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \hspace{.05\textwidth}%
    \begin{subfigure}[t]{.28\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
    }\label{fig:timing}
\end{figure*}
